Paper NA

### 2017-02-21 Paper_NA.tex
with geological map

As observed in \cite{gung2003global}; down to 250km low positive ($< 2\%$) anomalies of $dln(\xi)$ (Compared to an isotropic $\xi$) are observed in the whole craton. In contrast with the oceanic surrounding that shows strong positive anomalies ($> 4\%$). 
The gulf of Mexico and the southern part of Greenland show $\xi$ anomalies that are comparable to oceanic signature. 
The Grenville and Appalachian shelf (including the eastern Superior craton) show also higher $\xi$ anomalies comparable to oceanic signature. 
Deeper, positive anomalies are emerging beneath archaean Slave/Rae blocks/Eastern Superior and proterozoic North THO/Yavapai/Mazatzal/Great Rhyolites provinces, however $dln\xi$ anomalies remain low beaneath the archaean eastern Superior block. 
In the whole lithosphere, $\xi$ is higher than $1$ which means that $V_{SH} > V_{SV}$.

>>>>

As observed in \cite{gung2003global}; down to 250km low positive ($< 2\%$) anomalies of $dln(\xi)$ (Compared to an isotropic $\xi$) are observed in the whole craton. In contrast with the oceanic surrounding that shows strong positive anomalies ($> 4\%$). 
The gulf of Mexico and the southern part of Greenland show $\xi$ anomalies that are comparable to oceanic signature. 
The Grenville and Appalachian shelf (including the eastern Superior craton) show also higher $\xi$ anomalies comparable to oceanic signature. 
Deeper, positive anomalies are emerging beneath archaean Slave/Rae blocks/Eastern Superior and proterozoic North THO/Yavapai/Mazatzal/Great Rhyolites provinces, following highest velocities anomailies. However $dln\xi$ anomalies remain low beaneath the archaean eastern Superior block. 
In the whole lithosphere, $\xi$ is higher than $1$ which means that $V_{SH} > V_{SV}$.
